### 2018-01-31 includes/stringfuzz.tex
Removing minted for now.

\fuzzer{} can be used to
generate benchmark suites in a batch mode, or can be used in an online
randomized fashion for exploratory debugging. For example, \fuzzer{}
can be invoked as follows to feed random problems to \cvc{} until it
returns an error:
\vspace{-0.15in}
\begin{figure}[H]
    \centering
    \begin{minipage}[b]{0.91\linewidth}
        \begin{minted}{bash}
while \
  stringfuzzg -r random-ast -m \
  | tee problem.smt25 \
  | cvc4 --lang smt2.5 --tlimit=5000; do
    sleep 0
done
        \end{minted}
    \end{minipage}
\end{figure}
\vspace{-0.15in}

Some more \unix{} scripting can yield other interesting results. For
example, the following script finds a regex problem on which \us{}
times out after 5 seconds:
\vspace{-0.15in}
\begin{figure}[H]
    \centering
    \begin{minipage}[b]{0.91\linewidth}
        \begin{minted}{bash}
while true; do
    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
    result=`z3str3 -T:5 problem.smt25`
    echo $result
    if [ "$result" == "timeout" ]; then
        cat problem.smt25
        break
    fi
done
        \end{minted}
    \end{minipage}
\end{figure}
\vspace{-0.15in}

>>>>

\fuzzer{} can be used to
generate benchmark suites in a batch mode, or can be used in an online
randomized fashion for exploratory debugging. For example, \fuzzer{}
can be invoked as follows to feed random problems to \cvc{} until it
returns an error:
% \vspace{-0.15in}
% \begin{figure}[H]
%     \centering
%     \begin{minipage}[b]{0.91\linewidth}
%         \begin{minted}{bash}
{\scriptsize\begin{verbatim}
while \
  stringfuzzg -r random-ast -m \
  | tee problem.smt25 \
  | cvc4 --lang smt2.5 --tlimit=5000; do
    sleep 0
done\end{verbatim}}
%         \end{minted}
%     \end{minipage}
% \end{figure}
% \vspace{-0.15in}

Some more \unix{} scripting can yield other interesting results. For
example, the following script finds a regex problem on which \us{}
times out after 5 seconds:
% \vspace{-0.15in}
% \begin{figure}[H]
%     \centering
%     \begin{minipage}[b]{0.91\linewidth}
%         \begin{minted}{bash}
{\scriptsize\begin{verbatim}while true; do
    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
    result=`z3str3 -T:5 problem.smt25`
    echo $result
    if [ "$result" == "timeout" ]; then
        cat problem.smt25
        break
    fi
done\end{verbatim}}
%         \end{minted}
%     \end{minipage}
% \end{figure}
% \vspace{-0.15in}
